---
title: "615 Final Project"
author: "Donghao Xue"
date: "14/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(bizdays)
library(tidyquant)
```

## Introduction

In this project, I will use online investment advice that was available at the beginning of July 2020. to make investment decisions and then track my investments through the fall until 1 December. I choose three stocks and track the value of my portfolios.

Three portfolios I made: 

50% AAPL, 25% GOOG, 25% AMZN

25% AAPL, 50% GOOG, 25% AMZN

25% AAPL, 25% GOOG, 50% AMZN

## EDA

```{r}
#get individual asset returns grouped by asset
stock_returns <- c("AAPL", "GOOG", "AMZN") %>%
  tq_get(get  = "stock.prices",
         from = "2020-07-01",
         to   = "2020-12-02") %>%
  group_by(symbol) %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "daily", 
               col_rename = "Ra")

```

```{r message=FALSE, warning=FALSE}
#get baseline asset returns
baseline_returns <- "XLK" %>%
  tq_get(get  = "stock.prices",
         from = "2020-07-01",
         to   = "2020-12-02") %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "daily", 
               col_rename = "Rb")


```


```{r message=FALSE, warning=FALSE}
stock_returns_multi <- stock_returns %>%
    tq_repeat_df(n = 3)
```

### Weights table
```{r}
weights <- c(
    0.50, 0.25, 0.25,
    0.25, 0.50, 0.25,
    0.25, 0.25, 0.50
)
stocks <- c("AAPL", "GOOG", "AMZN")
weights_table <-  tibble(stocks) %>%
    tq_repeat_df(n = 3) %>%
    bind_cols(tibble(weights)) %>%
    group_by(portfolio)

weights_table

```


```{r}
portfolio_returns_multi <- stock_returns_multi %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = Ra, 
                 weights     = weights_table, 
                 col_rename  = "Ra")

```



```{r}
portfolio_growth_multi <- stock_returns_multi %>%
    tq_portfolio(assets_col   = symbol, 
                 returns_col  = Ra, 
                 weights      = weights_table, 
                 col_rename   = "investment.growth",
                 wealth.index = TRUE) %>%
    mutate(investment.growth = investment.growth * 250000)

```



```{r message=FALSE, warning=FALSE}
portfolio_growth_multi %>%
    ggplot(aes(x = date, y = investment.growth, color = factor(portfolio))) +
    geom_line(size = 2) +
    labs(title = "Portfolio Growth",
         subtitle = "Comparing Multiple Portfolios",
         x = "", y = "Portfolio Value",
         color = "Portfolio") +
    geom_smooth(method = "loess") +
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar)

```



### CAPM table
```{r}
RaRb_multiple_portfolio <- left_join(portfolio_returns_multi, 
                                     baseline_returns,
                                     by = "date")

```


```{r}
#create the CAPM table of multiple portfolios
RaRb_multiple_portfolio %>%
    tq_performance(Ra = Ra, Rb = Rb, performance_fun = table.CAPM)

```

The annual Alpha value for the three portfolios are 7%, 7% and -2% seperately.

## Analysis
```{r}
#Calculate profit and return rate of three multiple portfolios
d = which(portfolio_growth_multi$date == "2020-12-01")
profit1 = portfolio_growth_multi$investment.growth[d[1]] - 250000
profit2 = portfolio_growth_multi$investment.growth[d[2]] - 250000
profit3 = portfolio_growth_multi$investment.growth[d[3]] - 250000

rate_of_return_1 = profit1/250000
rate_of_return_2 = profit2/250000
rate_of_return_3 = profit3/250000

print(cbind(profit1, profit2, profit3))

print(cbind(rate_of_return_1, rate_of_return_2, rate_of_return_3))
```

## Conclusion 

For the three portfolios, I will choose the first one because it has the highest return rate and profit.


## Reference

Data is from : finance.yahoo.com




























